### 2024-06-25 basic-statistics.qmd
20240624 - tweaks

$$
\begin{aligned}
  d &= \frac{\text{mean difference}}{\text{pooled standard deviation}} \\
   &= \frac{X_1 - X_2}{s} \\
\end{aligned}
$$ {#eq-cohensD}

@@

The coefficient of determination ($R^2$) is the proportion of variance in the [outcome variable](#sec-correlationalStudy) that is explained by the [predictor variables](#sec-correlationalStudy).
\eta^2 is the proportion of variance in the [dependent variable](#sec-experiment) that is explained by the [independent variables](#sec-experiment).
The coefficient of determination and \eta^2 can be expressed as the ratio of variance explained in the [outcome](#sec-correlationalStudy) or [dependent](#sec-experiment) variable to the total variance in the [outcome](#sec-correlationalStudy) or [dependent](#sec-experiment) variable, as in @eq-coefficientOfDeterminationPartitionedVariance:

>>>>

$$
\begin{aligned}
  d &= \frac{\text{mean difference}}{\text{pooled standard deviation}} \\
   &= \frac{\bar{X_1} - \bar{X_2}}{s} \\
\end{aligned}
$$ {#eq-cohensD}

@@

The coefficient of determination ($R^2$) is the proportion of variance in the [outcome variable](#sec-correlationalStudy) that is explained by the [predictor variables](#sec-correlationalStudy).
$\eta^2$ is the proportion of variance in the [dependent variable](#sec-experiment) that is explained by the [independent variables](#sec-experiment).
The coefficient of determination and $\eta^2$ can be expressed as the ratio of variance explained in the [outcome](#sec-correlationalStudy) or [dependent](#sec-experiment) variable to the total variance in the [outcome](#sec-correlationalStudy) or [dependent](#sec-experiment) variable, as in @eq-coefficientOfDeterminationPartitionedVariance:
